Paper Figure Generation

### 2022-07-30 R/PaperFigureGeneration.rmd
HYV is better than YR!
Lots of changes to accommodate the change in sequence pattern from YR to HYV:
- Changed sequence frequency generation to except regular expression patterns.
- Updated various plotting and data generation notebooks to generate new HYV plots. This also included updating figure generation.

arabidopsisDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis")
arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")

yeastDataDirectory = file.path(deaminationDataDirectory, "yeast")
yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")

GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")

@@

XPCDataDirectory = file.path(deaminationDataDirectory, "XP-C")
XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
```

@@

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

```{r figure_4A, fig.width = 5, fig.height = 6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
                               xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```

@@

NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

@@

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
```
```{r figure_6B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

@@

```{r figure_S4, fig.width = 9, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered,
                               title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7,
                               xAxisLabel = "Mismatch Relative Position")
```

```{r read_figure_S5_data}
arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
    timepoint = names(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
    timepoint = names(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

```{r figure_S5, fig.width = 9, fig.height = 5}
plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = 10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```

```{r read_figure_S6_data}
NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
  ))
}

@@

```{r figure_S6, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative GG>AA Frequency")
```

>>>>

arabidopsisDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis")
arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")
arabidopsisGeneralReadSequenceDataDirectory = file.path(arabidopsisDataDirectory, "general_read_sequences")

yeastDataDirectory = file.path(deaminationDataDirectory, "yeast")
yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")
yeastGeneralReadSequenceDataDirectory = file.path(yeastDataDirectory, "general_read_sequences")

GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")
GM12878GeneralReadSequenceDataDirectory = file.path(GM12878DataDirectory, "general_read_sequences")

@@

XPCDataDirectory = file.path(deaminationDataDirectory, "XP-C")
XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")

EColiDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT")
EColiExcisionSiteDataDirectory = file.path(EColiDataDirectory, "excision_site_analysis")
EColiGeneralReadSequenceDataDirectory = file.path(EColiDataDirectory, "general_read_sequences")
```

@@

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))
NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
  ))
}
NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered = fread(generateFilePath(
  arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered = fread(generateFilePath(
  yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered = fread(generateFilePath(
  EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
```

```{r figure_4A, fig.width = 6.5, fig.height = 6}
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
                               xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4B, fig.width = 5, fig.height = 6}
# ### Just the 1h timepoint (asterisks) ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("333"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
#                         endBasedCheckPositions = -9, xAxisLabel = "Mismatch Relative Position",
#                         significanceAsteriskBreakpoints = c(1e-3, 1e-10, 1e-20))

## Just the 1h timepoint (full p-values) ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4C, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered[Position <= 7],
                        title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```
```{r figure_4D, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered[Position <= 7],
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 24, maxReadLength = 30, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```
```{r figure_4E, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered[Position <= 7],
                        title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 22, maxReadLength = 25, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```
```{r figure_4F, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered[Position <= 7],
                        title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 11, maxReadLength = 13, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```

@@

NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
  ))
}

@@

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
```
```{r figure_6B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
                        xAxisOffset = 1)

@@

```{r read_figure_S4_data}
NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered = fread(generateFilePath(
  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered"
))
```

```{r figure_S4, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered[Position <= 7],
                        title = "NHF1 6-4 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisOffset = 1)
plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered[Position <= 7],
                        title = "GM12878 cisplatin 90min Rep1 TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisOffset = 1)
```

```{r read_figure_S5_data}
NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
  ))
}

@@

```{r figure_S5, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative GG>AA Frequency")
```
